A thesis draft

### 2018-09-17 draft.tex
Little fixes and additions

In recent years, with the new hardware capabilities and the recent development 
of in-kernel virtualization systems (such as Hyper-V) this technology 
begin to be adopted. Virtualization allows to run different systems on the 
same machine, making them completely isolated and then more resilient to 
failure. The back of the medal, though, is that virtual machines requires large 
amount of resources, especially memory, because solutions like copy-and-write 
of in-memory pages are not viable anymore, leading to duplication of loaded 
libraries and assets in the memory of the host. For large deployment containing 
only simple services (e.g. a backend application serving a website or a 
database) this result in a waste of resources. \todo{Talk about lxc containers 
and how Docker solved magically the problem.}

@@

Starting with the first step of creating a MANO able to process incoming data 
packets through VNF functions, we encountered that many networking tools already 
present in the market required some tweaking and some integrations, shifting our 
goal to create a complete  European Telecommunications Standards Institutes 
(ETSI) Management and orchestrator (MANO) testbed instead, following the 
specifications suggested in the RFC 7665, thus implementing only the first three 
requisites, without digging in the satellite data flow optimization.
\end{document}

>>>>

In recent years, with the new hardware capabilities and the recent development 
of in-kernel virtualization systems (such as Hyper-V) this technology 
begin to be adopted. Virtualization allows to run different systems on the 
same machine, making them completely isolated and then more resilient to 
failure. The back of the medal, though, is that virtual machines requires large 
amount of resources, especially memory, because solutions like copy-and-write 
of in-memory pages are not viable anymore (since the Kernel gets duplicated 
too), leading to duplication of loaded libraries and assets in the memory of the 
host. For large deployment containing only simple services (e.g. a backend 
application serving a website or a database) this ends up in a waste of 
resources. \todo{Talk about lxc containers and how Docker solved magically the 
problem.} It's here that, in ??\todo{Find Docker date of birth}, Docker was 
created, basing its solution on an already existing product: Linux Container 
(LXC). From this framework, docker built an entire ecosystem, consisting in a 
client/server model giving the possibility for users to simply launch, scale and 
delete containers \todo{Talk about Docker-Machine}, a repository system where 
images, the snapshot of a defined image, can be stored and tagged, in a sort of 
system version control and of another additional solutions, called 
\textit{Docker Compose}, and \textit{Docker Swarm} to, respectively, orchestrate 
containers in a single node or a clustered system. \vspace{0.5cm}

@@

Starting with the first step of creating a MANO able to process incoming data 
packets through VNF functions, we encountered that many networking tools already 
present in the market required some tweaking and some integrations, shifting our 
goal to create a complete  European Telecommunications Standards Institutes 
(ETSI) Management and orchestrator (MANO) testbed instead, following the 
specifications suggested in the RFC 7665, thus implementing only the first three 
requisites, without digging in the satellite data flow optimization.

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\end{document}
